BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-05-01 SubsetRecords2CBG.rmd
data writeout for CHIC - ready, do a final manual review

```{r}
p <- './manuscript/data'

dat_sub <- read.csv(file.path(p, 'test_data.csv')) |>
  select(Collection_number, CBG_ACC_BOOL) |>
  mutate(CBG_ACC_BOOL = if_else(is.na(CBG_ACC_BOOL), TRUE, FALSE)) |>
  filter(CBG_ACC_BOOL == TRUE)

read.csv( file.path(p, 'processed', 'cleaned_data.csv') ) |>
  select(-CBG_ACC_BOOL) |>
  right_join(dat_sub)
```

>>>>

```{r}
p <- './manuscript/data/processed'

dat_sub <- read.csv(file.path(p, 'cleaned_data.csv')) |>
  mutate(CBG_ACC_BOOL = if_else(is.na(CBG_ACC_BOOL), TRUE, FALSE)) 
dat_sub <- data.frame( apply(dat_sub, 2, as.character) )

dat_manual <- read.csv(file.path(p, 'cleaned_data-problemchildren.csv')) |>
  mutate(CBG_ACC_BOOL = if_else(is.na(CBG_ACC_BOOL), TRUE, FALSE)) 
dat_manual <- data.frame( apply(dat_manual, 2, as.character) )

dat_out <- filter(dat_sub, ! Collection_number %in% dat_manual$Collection_number) |>
  bind_rows( dat_manual) |>
  filter(CBG_ACC_BOOL == 'TRUE') |>
  arrange(Collection_number)

write.csv(dat_out, file.path(p, 'CHIC-RCB-2025.csv'))
```

### 2025-05-01 manuscript/labels/skeleton.Rmd
data
data writeout for CHIC - ready, do a final manual review

```{r load data}
data <- read.csv('../data/processed/cleaned_data.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

@@

`r writer(data$Habitat)`. `r data$physical_environ`  
Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup

>>>>

```{r load data}
data <- #read.csv('../data/processed/cleaned_data.csv') |>
  read.csv('../data/processed/cleaned_data-problemchildren.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

@@

`r writer(data$Habitat)`. `r data$physical_environ`

Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup
